---
title: "ITEC 621 - Homework 1 - R Practice"
author: "Your Name"
date: "Month dd, yyyy"
output: html_document
---

<span style="color:blue">*Note: save this file with the name HW1_YourLastName.Rmd [or HW2, etc.) and complete your homework in it.*</span>

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)
```

Note: this is a template for HW1, but you should use a similar template for HW2, 3 and 4, and also for your final project. Treat this homework and your project as a report. Format it and present it in a way that is attractive, easy to follow and businesslike. All your work should be labeled, numbered (if appropriate) and introduced. Overall, you should follow a format like this:

**Question Number or Item. Title.** Brief narrative about the work done for this question number or project item.

```{r}
# Enter all your R code for this question or item.
```

**Next Question or Item.** Explanation or narrative

```{r}
# More R code
```


For example, for Homework 1 you could do something like this:

1. **Rectangle Area**

```{r}
```

2. **Loop**

```{r}
```

3. **Read .csv data file**

```{r}
```

4. **lm() model, all variables **

```{r}
```

5. **lm() model, 5 variables **

```{r}
```

6. **Object's class**

```{r}
```

7. **What do these classes mean?**

```{r}
```

8. **Income.vect**

```{r}
```

9. **Mean, minimum, maximum, standard deviation and variance**

```{r}
```

10. **Income.stats** 

```{r}
```

11. **Vector Names**

```{r}
```

12. **5% Inflation**

```{r}
```

13. **Income Boxplot**

```{r}
```

14. **Income by Gender Boxplot**

```{r}
```

15. **Plot Credit Rating vs. Income**

```{r}
```

16. **Credit Rating Histogram**

```{r}
```

17. **Credit Rating qqplot** 

```{r}
```

18. **Is data normally distributed? Why or why not?**

```{r}
```

19. **ggplot2 Histogram**

```{r}
```

20. **Dual Line Plot**

```{r}
```
